Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-07 draftfinalreport_v4.Rnw
11:17 update scenarios table to be read from a file, and update writing

In concordance with current measles knowledge, strategies that target the very young (<1 year old) are not effective, and our analyses of the vaccinated cases suggests a substantial proportion of vaccinated cases (\autoref{fig:ageandvac}) were vaccinated with a single vaccine around 1 year of age (\autoref{fig:vaccstat} and \autoref{fig:vaccstat_close}). Furthermore, it appears possible to reach the appropriate figure (28\% of currently na\"{\i}ve) by vaccinating all the currently na\"{\i}ve older population groups with lower coverage, in particular school age children and young adults. However, there are a number of different vaccination schemes that will lead to sufficient coverage and these are given in \autoref{table:coh_vac}. The appropriate cover could be reached by catch up vaccination of all school aged children.

\begin{table}[htdp]\small % saved as vaccine_proportions_Cohort
\begin{center}
\begin{tabular}{lrrrr}
\hline
Age range (yrs) & Proportion of na\"{\i}ve population\\
\hline
2--5 & 0.04\\
5--11 & 0.15\\
5--16 & 0.27\\
5--18 & 0.31\\
11--16 & 0.14\\
11--18 & 0.18\\
19--25 & 0.19\\
19--30 & 0.34\\
19--46 & 0.46\\
0--29 & 0.72\\
0--44 & 0.89\\
>8 & 0.8 \\ 
\hline
\end{tabular}
\end{center}
\caption{Proportion of the currently na\"{\i}ve New Zealand population that would be immunised if all na\"{\i}ve people in each age range were immunised. The estimated additional proportion of the population requiring immunisation is 28\%}
\label{table:coh_vac}
\end{table}%

>>>>

In concordance with current measles knowledge, strategies that target the very young (<1 year old) are not effective, and our analyses of the vaccinated cases suggests a substantial proportion of vaccinated cases (\autoref{fig:ageandvac}) were vaccinated with a single vaccine around 1 year of age (\autoref{fig:vaccstat} and \autoref{fig:vaccstat_close}). To reach the appropriate figure (54\% of currently na\"{\i}ve) by vaccination, there are a number of scenarios that approach this value, but targetting all the currently na\"{\i}ve older population groups with lower coverage or all school age children and young adults may be insufficient. However, there are a number of different vaccination schemes that will lead to sufficient coverage and these are given in \autoref{table:coh_vac}. These proportions will be lower if the proportion of equivocal serological results in adults are classified as immune, rather than na\"{\i}ve.

\begin{table}[hbtp] \scriptsize
\captionsetup{width=1\textwidth}
<<results=tex,echo=FALSE>>=
colnames(propvCohort)<-c("Age range (yrs)","Proportion naive")
latex(propvCohort, file="", table.env=FALSE,rowname=NULL)
@
\caption{Proportion of the currently na\"{\i}ve New Zealand population that would be immunised if all na\"{\i}ve people in each age range were immunised. The estimated additional proportion of the population requiring immunisation is 54\%}
\label{table:coh_vac}
\end{table}
